\cvsection{Employment}
\begin{cventries}

%---------------------------------------------------------
  \cventrypara
    {Senior Software Engineer} % Job title
    {LINE Corporation - MixRadio} % Organization
    {Bristol} % Location
    {2014  - Present} % Date(s)
    {With MixRadio being sold to LINE corporation by Microsoft my role was a continuation from that at Microsoft.}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I recently developed a full stack Clojure and ClojureScript service which enabled in house mixmasters to manually tweak MixRadio's recommendations engine.}
        \item {I Integrated SalesForce with MixRadio’s internal CRM system. A Clojure service which extracted all relevant data from Salesforce and parsed it to AWS SQS and persisted it to Redshift.}
        \item {I produced an EMR processing pipeline to transform our massive user taste profiles into a suitable format and export it to SalesForce for recommendation emails.}
        \item {I’ve written various Cascalog and Pigpen Big data flows over millions of user events to support and improve music recommendations eg find and boost emerging “hot” tracks.}
      \end{cvitems}
    }

  \cventrypara
    {Senior Software Engineer} % Job title
    {Microsoft} % Organization
    {Bristol} % Location
    {2013  - 2014} % Date(s)
    {Microsoft purchased Nokia's mobile business. My work was focused even more on the core music recommendations of the business building fault-tolerant, performant Clojure services and data processing at scale.}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Played a key role in creating a complex music recommendation service for similarly liked tracks and artists. This replaced the 3rd party reliance on The EchoNest. Built with Clojure on DynamoDB.}
        \item {I built a highly performant microservice to match track and artist metadata to MixRadios internal representation.}
        \item {I created a service to warehouse client user events from Kafka to S3, encrypting any sensitive user data.}
        \item {I designed and produced a service to produce new album release events no notify intrested users, in Clojure on MongoDB.}
        \item {I built up the majority of MixRadios client ’views’ API, it produced customised views of JSON data allowing clients to build their pages, coded in Java and Spring.}
        \item {A key contributor to MixRadios core services:
            \begin{itemize}
                \item Users music taste profile service, based on MongoDB in Clojure.
                \item An API to serve session based curated mixes, in Clojure and Redis.
                \item The music catalogue and search engine, based on Java, MySQL and Apache Solr.
            \end{itemize}}
      \end{cvitems}
    }

  \cventrypara
    {Senior Software Engineer} % Job title
    {Nokia } % Organization
    {Bristol} % Location
    {2009  - 2013} % Date(s)
    {During my time at Nokia I transitioned from automated tester, to a full time Java and then Clojure developer. My role from newest to oldest:}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\emph{Developer:} Designed and built key services to provide mobile phone notifications to millions of users.}
        \item {\emph{Developer:} In 2012, I joined a small team working on Nokia's first production Clojure services with the ultimate aim to replace our 3rd party integration with The EchoNest.}
        \item {\emph{Developer:} Nokia ceased to support Meego and I moved into full-time Java development. I was one-half of a pair that integrated with a 3rd party company, The EchoNest. Integrating their music recommendations produced Nokia music’s first iteration of its internet radio (later to be called MixRadio). This was a Java and Spring based service.}
        \item {\emph{Build Manager:} I became the Bristol office's package manager for the Meego (Linux-based) operating system. I was responsible for integrating Bristol's music software into the Debian based operating system via apt package management.}
        \item {\emph{Testing:} Developed both a front end web test frameworks around JBehave and Selenium2. An also a  FitNesse suite to test a large scale music search engine. This mainly involved writing fixtures in Java to enable less technical testers to write wiki based tests.}
      \end{cvitems}
    }

  \cventrypara
    {Senior Automated Test Engineer} % Job title
    {Alterian} % Organization
    {Bristol} % Location
    {2008  - 2009} % Date(s)
    {A UK-based supplier of marketing automation software and services. I was their sole automated tester and worked on their “Next Generation” web-based platform.}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web test framework based on Selenium, Selenium Grid, and Gallio/MbUnit 3 running on EC2.}
        \item {Implemented a JMeter Test Suite.}
      \end{cvitems}
    }

  \cventrypara
    {Senior Automated Test Engineer} % Job title
    {Experian (Decision Analytics EMEAI)} % Organization
    {Bristol} % Location
    {2006  - 2008} % Date(s)
    {Talgentra was acquired by Experian, I progressed into a more senior automated testing role.}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Test framework based around FitNesse and Watir written in Java. }
        \item {Administering the QA departments testing environments; large array of pre-configured virtual machines.}
        \item {Aided in conducting interviews, took responsibility of the QA department in the absence of the QA manager.}
      \end{cvitems}
    }

  \cventry
    {Junior Software Engineer } % Job title
    {Talgentra} % Organization
    {Bristol} % Location
    {2004 - 2006} % Date(s)
    {Talgentra produced utility billing software for electricity, water, gas and telecommunications. This was my initial introduction to Java, writing some Junit and automated acceptance tests.
    }
\end{cventries}
