\documentclass{statement}

\Title{Statement of Purpose}
\Name{Chengxiang Ren}
\Email{irhawks@hotmail.com}
\Web{}
\University{Hainan University}

\begin{document}

\maketitle

I graduated from xxx university with a degree in xxx (subject). I would like to apply xxx at your university. With my great passion in the area, I hope to become an expert in xxxx industry. I understand that xxxx university is famous for xxxx, it has established a great reputation in the xxx industry with lots of graduates from becoming leaders in the field. I want to become one of them, and therefore, I am very interested and keen to be involved in your university

My preparation for your programme has been expansive and thorough. First, I have a solid background in xxx and xxx. Second, during my undergraduate years, I joined a club called xxx with the focus on xxx. Our projects dealt with xxx, and other xxx. My work outside the campus, in job placements through xxx university, granted me excellent opportunities for real-world experience.

While exploring the possibility of graduate-level work, I discovered that my interests are perfectly matched with your programme. My interest in xxx, especially, was piqued during my xxx class. The aspects of the xxx fascinated me and made me long to supervise a large project in this field one day. Although I realise my current limitations, my whole-hearted enthusiasm, combined with guidance from your exceptional faculty, will carry me through the rigors of studying and forge me into an expert xxx after the one/two year master course and the subsequent Ph.D. course.

\statement{Conclusion} 
Upon graduation from your school, I plan to work as a xxx in a xxx company or as a researcher at an institute. Participating in the development of xxx would fulfil my aspirations. In the long term, I would like to become a professor in order to share my knowledge and experience and instruct the next generation of xxx.

%\statement{Project \#1}
%Morbi sed sapien ut ante elementum luctus vitae et libero. Praesent
%felis enim, elementum nec suscipit non, suscipit a diam. Nulla
%vulputate facilisis orci, vel iaculis odio feugiat id. Fusce in dolor
%interdum ante dignissim bibendum. Nullam euismod interdum commodo.
%Etiam a mauris ac purus dignissim ultrices at eu nisl. Suspendisse
%varius ipsum eu massa ullamcorper in convallis nulla vulputate.
%
%\statement{Project \#2}
%Nulla non mauris quis mi pellentesque interdum. Sed venenatis pretium
%sem sed pretium. Pellentesque et augue velit, ut bibendum leo. Proin
%congue nisl id leo tristique sagittis. Curabitur id diam in turpis
%faucibus pharetra eget elementum orci. Sed vel nunc nibh. Praesent non
%enim eros, sed convallis dui. Pellentesque accumsan viverra dolor sed
%luctus.
%
%Sed non posuere leo. Curabitur eu est ut tellus ultrices ornare quis
%ut tortor. Aliquam faucibus mauris in leo tincidunt euismod. Aliquam
%lacinia euismod dolor, tempus gravida erat facilisis elementum.
%Pellentesque pretium pharetra orci, eu consequat arcu dapibus et.
%Quisque quis dolor magna. Fusce gravida risus at ipsum lobortis id
%facilisis justo malesuada. Donec egestas placerat congue. Curabitur
%eget diam at odio iaculis pellentesque quis in est. Aenean sit amet
%sodales tortor. Morbi a nulla magna.
%
%\statement{Conclusion}
%Praesent vel mi pharetra justo lacinia consectetur. In in odio neque.
%Donec in tellus nulla, quis fringilla quam. In hac habitasse platea
%dictumst. In hac habitasse platea dictumst. Maecenas nisi elit, dictum
%at fringilla vitae, vestibulum vitae ligula. Vestibulum ante ipsum
%primis in faucibus orci luctus et ultrices posuere cubilia Curae; Duis
%placerat ipsum sit amet ante fermentum condimentum. Nunc facilisis
%eros euismod nisl euismod id egestas turpis imperdiet. Etiam
%consectetur risus vitae augue scelerisque in fringilla odio
%vestibulum. Ut venenatis convallis suscipit. Maecenas cursus dignissim
%semper. Vestibulum tempor lectus vel justo consequat vel faucibus enim
%viverra. Donec nunc ligula, luctus nec molestie eget, aliquam vel
%lectus.

\end{document}
